\textcolor{blue}{A gradient-based optimization method for motion planning}$^{1}$

### 2016-01-18 paper.tex
Use Linearly Constrained Quadratic Problem instead of Quadratic Program
  QP -> LCQP

The idea of our method is to find a good trade-off between
the simplicity of “blind” methods like shortcut algorithms,
and the complexity of distance based optimization techniques.
The method iteratively shortens the initial path with gradient-based information.
When a collision is detected at a given iteration, the method backtracks to the
latest valid iteration and inserts a one-dimensional constraint
between the objects detected in collision. Only collisions between objects are 
evaluated, therefore no pre-processing of either the
robot or environment models is necessary to increase distance computation speed. 
Respecting the problem geometry also 
preserves that a solution can still be found, e.g. for narrow passages as holes or 
grippers. The method is also repeatable since no randomness is introduced. The underlying optimization algorithm is a quadratic program.

@@

\textcolor{blue}{This section describes the settling of the Gradient-based optimizer. The method works as a classical Quadratic Program (QP), reducing the path length with a cost function and avoid collisions with constraints. Details of the QP elements will be given in the following subsections, and associated to functions that will populate the global algorithm, presented in the last section.}

@@

Finally, we refer to~\cite{nocedal2006numerical} for solving constrained quadratic 
programs (QP). \textcolor{blue}{The QP step computation corresponds to a constrained 
version of \texttt{computeIterate}}.

@@

In this section, the GB path-optimizer Algorithm~\ref{algo:gradient} is described
according to the previous steps definitions.
\textcolor{blue}{Remind that, the QP optimal step $\p$ computed by \texttt{computeIterate} is known.
The idea of the algorithm is to process iterations that reduce the path length according to the QP cost. If collision-constraints have been added to the QP, further iterations will comply with them. The algorithm stops whether the QP minimum is reached and collision-free. The collision detection on a path is handled by \texttt{validatePath}, which returns $true$ if the given path is collision-free.
}

@@

Optimization computation time and path length averages are presented for 30 runs of 
each example in (Table~\ref{tab:results}). In some cases, $\alpha_{init}$ was 
reduced to comply with very narrow passages, or increased in the opposite case. 
On the one hand, for non-high DOF examples, it appears that computation time is higher using the GB 
optimization. The worst case comes out for the puzzle problem where the number of 
constraints of GB is significant and $\alpha_{init}$ reduced. 
In addition, collision checking is rapidly processed in such basic problem geometry. This favors RS while the GB optimizer spends time on the QP resolution to avoid collisions.
On the other hand, our method almost always provides the shortest paths, whereas it 
is not even the best criterion to quantify the parasite motions disappearance.
Note that these results are the consequence of the termination conditions of RS and PRS, balancing length reduction or shorter computation time. 
This is particularly visible for PRS which 
easily gives up in some problems, such as the 2D sliding-robot, the 
UR5-with-spheres or the puzzle.
Finally, the complete vanishing of the mobile base motion in the PRS and GB 
optimized paths is highlighted in the right column of (Table~\ref{tab:results}). 
Thus the issue addressed in Figure~\ref{decoupled_DOF_optimization} is 
solved considering this DOF.

\section{CONCLUSIONS}
We managed to settle a path optimization for navigation and manipulation problems, and tested it with various robots and environments. Our algorithm uses standard 
numerical tools as collision checking, linearized one-dimensional constraint
and QP resolution. It correlates them in a 
simple but effective way, and the algorithm structure is organized so that its 
convergence is guaranteed. Furthermore, 
our method only requires collision checking, therefore neither 
geometry pre-processing nor 
offline optimization are necessary to remain time-competitive. We demonstrate 
that the optimizer may be 
time-competitive compared to random shortcut in complex models where collision tests 
are time-consuming. 
It also proposes better quality paths, reducing the path length and removing 
unnecessary DOF motions. 
Finally, our optimizer manages to reduce a local detour in a long path while random 
shortcut methods will mostly fail.

>>>>

The idea of our method is to find a good trade-off between
the simplicity of “blind” methods like shortcut algorithms,
and the complexity of distance based optimization techniques.
The method iteratively shortens the initial path with gradient-based information.
When a collision is detected at a given iteration, the method backtracks to the
latest valid iteration and inserts a one-dimensional constraint
between the objects detected in collision. Only collisions between objects are 
evaluated, therefore no pre-processing of either the
robot or environment models is necessary to increase distance computation speed. 
Respecting the problem geometry also 
preserves that a solution can still be found, e.g. for narrow passages as holes or 
grippers. The method is also repeatable since no randomness is introduced. The underlying optimization algorithm is a \textcolor{blue}{linearly constrained} quadratic program.

@@

\textcolor{blue}{This section describes the settling of the Gradient-based optimizer. The method works as a classical Linearly Constrained Quadratic Program (LCQP), reducing the path length with a cost function and avoid collisions with constraints. Details of the LCQP elements will be given in the following subsections, and associated to functions that will populate the global algorithm, presented in the last section.}

@@

Finally, we refer to~\cite{nocedal2006numerical} for solving constrained quadratic 
programs (\textcolor{blue}{LC}QP). \textcolor{blue}{The step computation corresponds to a constrained 
version of \texttt{computeIterate}}.

@@

In this section, the GB path-optimizer Algorithm~\ref{algo:gradient} is described
according to the previous steps definitions.
\textcolor{blue}{Remind that, the LCQP optimal step $\p$ computed by \texttt{computeIterate} is known.
The idea of the algorithm is to process iterations that reduce the path length according to the LCQP cost. If collision-constraints have been added to the LCQP, further iterations will comply with them. The algorithm stops whether the LCQP minimum is reached and collision-free. The collision detection on a path is handled by \texttt{validatePath}, which returns $true$ if the given path is collision-free.
}

@@

Optimization computation time and path length averages are presented for 30 runs of 
each example in (Table~\ref{tab:results}). In some cases, $\alpha_{init}$ was 
reduced to comply with very narrow passages, or increased in the opposite case. 
On the one hand, for non-high DOF examples, it appears that computation time is higher using the GB 
optimization. The worst case comes out for the puzzle problem where the number of 
constraints of GB is significant and $\alpha_{init}$ reduced. 
In addition, collision checking is rapidly processed in such basic problem geometry. This favors RS while the GB optimizer spends time on the \textcolor{blue}{LC}QP resolution to avoid collisions.
On the other hand, our method almost always provides the shortest paths, whereas it 
is not even the best criterion to quantify the parasite motions disappearance.
Note that these results are the consequence of the termination conditions of RS and PRS, balancing length reduction or shorter computation time. 
This is particularly visible for PRS which 
easily gives up in some problems, such as the 2D sliding-robot, the 
UR5-with-spheres or the puzzle.
Finally, the complete vanishing of the mobile base motion in the PRS and GB 
optimized paths is highlighted in the right column of (Table~\ref{tab:results}). 
Thus the issue addressed in Figure~\ref{decoupled_DOF_optimization} is 
solved considering this DOF.

\section{CONCLUSIONS}
We managed to settle a path optimization for navigation and manipulation problems, and tested it with various robots and environments. Our algorithm uses standard 
numerical tools as collision checking, linearized one-dimensional constraint
and \textcolor{blue}{LC}QP resolution. It correlates them in a 
simple but effective way, and the algorithm structure is organized so that its 
convergence is guaranteed. Furthermore, 
our method only requires collision checking, therefore neither 
geometry pre-processing nor 
offline optimization are necessary to remain time-competitive. We demonstrate 
that the optimizer may be 
time-competitive compared to random shortcut in complex models where collision tests 
are time-consuming. 
It also proposes better quality paths, reducing the path length and removing 
unnecessary DOF motions. 
Finally, our optimizer manages to reduce a local detour in a long path while random 
shortcut methods will mostly fail.
